%-------------------------
% Resume in Latex
% Author : Kevin Wegman
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kevin Wegman} & Email : \href{mailto:kevinwegman1993@gmail.com}{kevinwegman1993@gmail.com}\\
  Senior Software Developer & Mobile : \href{tel:+16148433789}{+1-614-843-3789} \\
\end{tabular*}


%-----------Objective-----------------
\section{Objective}
  {Creative and dedicated engineer with extensive software development experience and passion for developing skills to improve my problem solving capabilities. Seeking an opportunity where my experience leading development of complex applications with multidisciplinary teams can provide value.}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {The Cadmus Group (Supporting USDA)}{Remote}
    {Senior Full-Stack Geospatial Software Developer}{February 2025 - Present}
    \resumeItemListStart
      \resumeItem{Geospatial Data Asset Catalog Team Lead}
        {Lead team of seven developers and data scientists in creation of application for USDA to manage geospatial assets. Architect solution to allow asynchronous data synchronization from multiple sources using an event driven approach. Responsible for establishing CI/CD pipelines to deploy application to various deployment environments. }
      \resumeItem{Data Distribution and Synchronization Working Group Technical Lead}
        {Serve as technical lead for the working group responsible for establishing data distribution and synchronization patterns for implementation across the solution team. Plan technical topics, guide documentation generation, and support research into requirements across the solution team. Develop presentations and technical documentation for patterns to problems with various requirements. }
    \resumeItemListEnd

  \resumeSubheading
    {Quantum Health}{Columbus, OH}
    {Senior Software Developer}{November 2023 - February 2025}
    \resumeItemListStart
      \resumeItem{Integrated Application Development}
        {Designed, implemented and tested an SSO system to significantly reduce new client onboarding and existing client maintenance overhead. The system supports integration with over 90 vendors and experiences millions of annual users. The new system was developed with a microservices architecture deployed to AWS with a PostgreSQL datastore, a VueJS UI, and multiple ASP.NET core APIs. }
      \resumeItem{Data Integration}
        {Design and maintain multiple data integration systems through event based (Apache Kafka) monitoring. Developed pipelines for data integration through AWS lambdas with Kafka event monitors, as well as custom data migration and analysis scripts. Architected event monitoring logs to track SSO usage and issues, and assisted in monitoring / resolution based on log information. }
    \resumeItemListEnd

    \resumeSubheading
      {Battelle Memorial Institute}{Columbus, OH}
      {Senior Data Scientist}{Feb 2016 - Aug 2023}
      \resumeItemListStart
        \resumeItem{Development Lead}
          {Serve as development lead for \$10+ million annual project providing data analysis, modeling and simulation, and application development to analyze the risk of Chemical, Biological, Radiological, Nuclear and Explosive (CBRNE) terrorism attacks. Develop complex Monte-Carlo based computational models to assess CBRNE terrorism risk by collaborating with multi-disciplinary teams to adapt existing algorithms and methodologies with novel approaches.}
        \resumeItem{Requirement Management}
          {Work with government clients, stakeholders and internal product consumers to identify areas for capability expansion; architect and drive solutions for expansion of those capabilities resulting in more stable and maintainable processes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Ohio State University}{Columbus, OH}
      {Master of Science in Nuclear Engineering;  GPA: 3.9}{Aug 2014 -- May 2016}
    \resumeSubheading
    {The Ohio State University}{Columbus, OH}
    {Bachelors of Science in Chemical Engineering;  GPA: 3.7}{Aug 2011 -- Dec 2014}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
    \textbf{Languages}{: C\#, C++, Python, SQL, JavaScript, Typescript, HTML/CSS, Java, Rust, XML, JSON, YAML} \\
    \textbf{Frameworks and Libraries}{: ASP.NET, VueJS, ReactJS, NUnit, Moq, Vitest, Axios, Electron, Vuetify, Entity Framework, Razor, Dapper, SQLAlchemy, Liquibase, MSSQL, PostgreSQL, PostGIS, Kafka, GDAL, GEOS} \\
    \textbf{Developer Tools}{: Visual Studio, Git, Docker, Azure Devops, Github AE, Azure Portal, AWS Console, VS Code, Jetbrains IDEs, PGAdmin, DBeaver, ArcGIS, QGIS}
   }}
\end{itemize}


%-------------------------------------------
\end{document}